# Data Analysis - QC mix

```{r}
#| output: false
#| warning: false

#Data is importer for the two data set (mzmine and ms_dial). A reference data frame is constructed (unifi) as well as data frame with theoretical values (qc_compounds)

#library(readr)
#library(readxl)

mzmine <- read_excel("~/Project/hrms_converter-2024/qc5rep_hdmse_peakpicking_featurelist_MZMINE.xlsx", 
    col_types = c("text", "text", "numeric", 
        "numeric", "text", "text", "numeric", 
        "numeric", "text", "numeric", "numeric", 
        "text", "text", "text", "text", "text", 
        "text", "text", "numeric", "text", 
        "text", "text", "text", "text", "numeric", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "numeric", 
        "numeric", "numeric", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "numeric", "numeric", "numeric", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "numeric", 
        "numeric", "numeric", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "numeric", "numeric", "numeric", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "numeric", 
        "numeric", "numeric"))

ms_dial <- read_excel("~/Project/hrms_converter-2024/qc3rep_hdmse_peakpicking_featurelist_MSDIAL.xlsx")

unifi <- data.frame(compound=c("acetaminophen","caffeine","leucine enkephaline","reserpine","sulfadimethoxine","sulfaguanidine","terfenadine","val-tyr-val","verapamil")
  , mz_unifi=c(152.0697, 195.0870, 556.2756, 609.2787, 311.0801, 215.0589, 472.3197, 380.2173, 455.2892),
  rt_unifi=c(0.56,1.30,2.37,3.37,2.96,0.31,3.66,1.28,3.26),
  dt_unifi=c(2.26,2.60,6.41,7.23,4.00,3.01,6.48,5.05,5.66))

qc_compounds <- data.frame(
  compound=c("acetaminophen","caffeine","leucine enkephaline","reserpine","sulfadimethoxine","sulfaguanidine","terfenadine","val-tyr-val","verapamil")
  , mz=c(152.0705, 195.0876, 556.2765, 609.2806, 311.0808, 215.0597, 472.3209, 380.2179, 455.2904))
```

```{r}
#Creating new obects with only the part of the data for both data sets. RT and Mobility is rounded to two digits to be compariable to unifi data

#Only keep rows that corresponds to the compounds in qc_compounds
mzmine_subset <- mzmine |> 
  select(id,height,ion_mobility,rt,mz) |> 
  mutate(across(c(rt,ion_mobility),round, 2)) |> 
  mutate(across(mz,round, 4)) |>
  filter(id %in% qc_compounds$compound )

#msdial data is filtered to excluded the rows where mobility is -1.00
#Also only keep rows that corresponds to the qc compounds
msdial_subset <- ms_dial |> 
  select(`Alignment ID`,Average,`Average Rt(min)`,`Average mobility`,`Average Mz`) |> 
  mutate(across(c(`Average Rt(min)`,`Average mobility`),round, 2)) |> 
  mutate(across(`Average Mz`,round, 4)) |>
  filter(`Average mobility` != -1.00 & `Alignment ID` %in% qc_compounds$compound )
```

------------------------------------------------------------------------

------------------------------------------------------------------------

Instead of manually add which features corresponds to the target compounds, can try filter the data sets (mzmine and msdial) for the compounds in unifi according to the retention time (RT), drift time (DT), and Mass-To-Charge ration(*m/z*).

|                                                                                                                                                                     |
|------------------------------------------------------------------------|
| [R for Data Science (2e) - 19  Joins (hadley.nz)](https://r4ds.hadley.nz/joins.html)                                                                                |
| "Mutating joins, which add new variables to one data frame from matching observations in another." e.g. `left_join()` and `inner_join()`                            |
| "Filtering joins, which filter observations from one data frame based on whether or not they match an observation in another." e.g. `semi_join()` and `anti_join()` |

```{r}
#library(tidyverse)
##library(readxl)
mzmine <- read_csv("~/Project/hrms_converter-2024/qc5rep_hdmse_peakpicking_featurelist_MZMINE.csv",show_col_types = FALSE)
glimpse(mzmine)

msdial <- ms_dial <- read_excel("~/Project/hrms_converter-2024/qc3rep_hdmse_peakpicking_featurelist_MSDIAL.xlsx") 

mzmine |> filter(is.na(rt) | is.na(mz) | is.na(ion_mobility)) #check that there are no missing values. Need to have entries for each obesrvation
mzmine |> count(rt, mz, ion_mobility) |> filter(n>1) #check that the variables uniquely identifies each feature

msdial |> filter(is.na(`Average Rt(min)`) | is.na(`Average Mz`) | is.na(`Average mobility`)) #check that there are no missing values. Need to have entries for each obesrvation
msdial |> count(`Average Rt(min)`, `Average Mz`, `Average mobility`) |> filter(n>1) #check that the variables uniquely identifies each feature
```

To combine two data frames by using the `join` -functions (`left_join()`, `inner_join()`, `right_join()`, `full_join()`, `semi_join()`, `anti_join()`) in `dplyr` -packages.

`left_join()`: output will have the same number of rows as input data frame x.

```{r}
mzmine2 <- mzmine #copied the data frames only for testing purposes
unifi2 <- unifi
msdial2 <- msdial

#MsDial data does not have mz and rt ranges as MzMine data has, therefore added manually
msdial2$mz_min <- msdial2$`Average Mz`-0.005
msdial2$mz_max <- msdial2$`Average Mz`+0.005
msdial2$rt_min <- msdial2$`Average Rt(min)`-0.08
msdial2$rt_max <- msdial2$`Average Rt(min)`+0.08

#finds the compounds in unifi in the mzmine data
subset_mzmine <- unifi2 |> inner_join(mzmine2, join_by(overlaps("mz_unifi","mz_unifi","mz_range:min", "mz_range:max"),overlaps("rt_unifi","rt_unifi","rt_range:min", "rt_range:max"))) |> 
  filter(abs(dt_unifi - ion_mobility) < 2) 

#subset_msdial <- unifi2 |> inner_join(msdial2, join_by(overlaps("mz_unifi","mz_unifi","mz_min", "mz_max"),overlaps("rt_unifi","rt_unifi","rt_min", "rt_max"))) |> filter(abs(dt_unifi - `Average mobility`) < 1.7) 

#finds the compounds in unifi in the msdial data
subset_msdial <- unifi2 |> 
  inner_join(msdial2, join_by(overlaps("mz_unifi","mz_unifi","mz_min", "mz_max"),overlaps("rt_unifi","rt_unifi","rt_min", "rt_max"))) |> 
  group_by(mz_unifi) |> 
  mutate(dt_diff = abs(dt_unifi - `Average mobility`)) |> 
  filter(dt_diff <=min(dt_diff))

no_duplicates_msdial <- subset_msdial[!duplicated(subset_msdial$compound), ] #removes the second duplicate feature
```

$MassError[ppm]=\frac{\textit{m/z}_{theretical}-\mathit{m/z}_{measured}}{\mathit{m/z}_{theoretical}}*10^6$

```{r}
#function to calculate the mass error 
mass_error <- function(mz_theoretical,mz_meaured){
  mass_error <- (mz_theoretical-mz_meaured)/mz_theoretical*10^6
  return(mass_error)
}

mass_error(qc_compounds$mz,subset_mzmine$mz)
mass_error(qc_compounds$mz,no_duplicates_msdial$`Average Mz`)
```

------------------------------------------------------------------------

------------------------------------------------------------------------

```{r}
#calculate the mass accuracy for mzmine, msdial, and unif based on the qc_compounds values. First the m/z values are sorted from small to large so the calculations can be performed row-wise for the correct compound. Lastly, the results are added to a column in a new object.

qc_compounds <- arrange(qc_compounds, mz)

mass_errors <- as.data.frame(qc_compounds[1:2])

mzmine_subset <- mzmine_subset |> arrange(mz) |> mutate(Mass_error_ppm = round((qc_compounds$mz-mz)/qc_compounds$mz*10^6,3))

msdial_subset <- msdial_subset |> arrange(`Average Mz`) |> mutate(Mass_error_ppm = round((qc_compounds$mz - `Average Mz`) /qc_compounds$mz * 10^6,3))

unifi <- unifi |> arrange(mz_unifi) |> mutate(Mass_error_ppm = round((qc_compounds$mz - mz_unifi) /qc_compounds$mz * 10^6,3))


mass_errors$Mzmine <- mzmine_subset$Mass_error_ppm
mass_errors$MsDial <- msdial_subset$Mass_error_ppm
mass_errors$Unifi <- unifi$Mass_error_ppm

#Adds a column that tells if the Mzmine or MsDial Mass errors are close or far away from the error of Unifi
mass_errors <- mass_errors |> mutate(mzmine_fromunifi = case_when(abs(Unifi - Mzmine) > 2 ~ "Large",
                                                   abs(Unifi - Mzmine) <= 2 & abs(Unifi - Mzmine) > 0.3 ~ "Medium",
                                                   abs(Unifi - Mzmine) <= 0.3 ~ "Small")) |> 
  mutate(msdial_fromunifi = case_when(abs(Unifi - MsDial) > 2 ~ "Large",
                                                   abs(Unifi - MsDial) <= 2 & abs(Unifi - MsDial) > 0.3 ~ "Medium",
                                                   abs(Unifi - MsDial) <= 0.3 ~ "Small"))
  
```

```{r}
#Plot the ms
mass_errors$msdial_fromunifi <- as.factor(mass_errors$msdial_fromunifi)
mass_errors$mzmine_fromunifi <- as.factor(mass_errors$mzmine_fromunifi)
  
p <- ggplot(data=mass_errors, mapping=aes(x=mz))+
  geom_point(aes(y=Mzmine, colour="Mzmine", shape="Mzmine", size=mzmine_fromunifi), alpha = 0.7)+
  geom_point(aes(y=MsDial, colour="MsDial", shape="MsDial", size=msdial_fromunifi), alpha = 0.7)+
  geom_line(aes(y=Unifi, colour="Unifi"),size=0.5)+
  
  scale_size_manual(name="Distance from Unifi", values = c("Large"=4.2, "Medium"=2.8, "Small"=2))+
  scale_shape_manual(values = c("Mzmine" = 19, "MsDial" = 17)) +
  scale_colour_manual(values = c("Mzmine" = "darkred", "MsDial" = "black", "Unifi" = "darkgrey")) + #colours of points
  labs(fill = "", y = "Mass Accuracy [ppm]", x=expression(paste("Theoretical ",italic("m/z"), " values"))) +
  
  geom_hline(yintercept = 0, linetype = "dashed", color = "red", linewidth = 0.1) + #adds horzontal line at y=0
  
  theme_minimal()+
  theme(
    panel.background = element_rect(fill = "white"),  # Set white background
    panel.grid = element_blank(),  # Remove grid lines
    axis.text = element_text(size = 9),  # Increase font size of axis text
    axis.title.y = element_text(size = 9,face = "bold"),  # Make y-axis label bold and italic
    axis.text.y = element_text(color = "black", size = 9),  # Make x-axis text bold
    axis.title.x = element_text(size = 10,face = "bold"),
    axis.text.x = element_text(color = "black", size = 9),  # Make x-axis text bold
    axis.ticks.x = element_line(color = "black"),  # Add ticks to x-axis in black color
    axis.ticks.y = element_line(color = "black"),  # Add ticks to y-axis in black color
    aspect.ratio = 0.5,  # Set aspect ratio
    plot.margin = margin(0.5, 0.5, 0.4, 0.5, "cm"),  # Set plot margins
    legend.text=element_text(size=9),
    legend.position = "right",
    legend.background = element_rect(fill="white",
                                   size=0.5, linetype="solid", 
                                   colour ="black"),
    #legend.title = element_blank(), #removes the title of the legend
    legend.title = element_text(size=9),
    legend.margin = margin(0.001, 1, 0.5, 0.5),)

p  + geom_text(aes(x=mz+10, y=Unifi,label=compound), size=2, colour="red4",
               nudge_x = 0.25, nudge_y = 0.25, 
               check_overlap = FALSE) #adds a text for the mean point

#+ guides(size = "none")

```

```{r}
#RT and DT difference between MS-Dial and Mzmine compared to UNIFI

#adding and then renaming the RT columns from each file
rt_difference <- data.frame(qc_compounds[,], msdial_subset[,3], mzmine_subset[,4], unifi[,3]) |> rename(MsDial_RT="Average.Rt.min.", MzMine_RT="rt", Unifi_RT="unifi...3.")
#adding and then renaming the DT columns from each file
dt_difference <- data.frame(qc_compounds[,], msdial_subset[,4], mzmine_subset[,3], unifi[,4]) |> rename(MsDial_DT="Average.mobility", MzMine_DT="ion_mobility", Unifi_DT="unifi...4.")


#rt_difference <- rt_difference |> mutate(mzmine_fromunifi = case_when(abs(Unifi - Mzmine) > 2 ~ "Large",
#                                                   abs(Unifi_RT - MzMine_RT) <= 2 & abs(Unifi_RT - MzMine_RT) > 0.3 ~ "Medium",
#                                                   abs(Unifi_RT - MzMine_RT) <= 0.3 ~ "Small")) |> mutate(msdial_fromunifi = case_when(abs(Unifi_RT - MsDial_RT) > 2 ~ "Large",
#                                                   abs(Unifi_RT - MsDial_RT) <= 2 & abs(Unifi_RT - MsDial_RT) > 0.3 ~ "Medium",
#                                                   abs(Unifi_RT - MsDial_RT) <= 0.3 ~ "Small"))

rt_difference_long <- rt_difference |> pivot_longer(cols = 3:5,
                            names_to = "Software",
                            values_to = "RT_softwares") 

dt_difference_long <- dt_difference |> pivot_longer(cols = 3:5,
                            names_to = "software_name",
                            values_to = "DT_softwares") 
```

```{r}
rt_difference_long |> filter(Software != "MsDial_RT" & Software != "MzMine_RT")
```

```{r}
#Plot of RT vs theoretical m/z values for the different softwares
b <- ggplot(data=rt_difference_long, mapping=aes(x=mz, y=RT_softwares))+
  geom_bar(stat = "identity",position=position_dodge(), aes(fill=Software))+
  
  scale_fill_manual(values = c("MzMine_RT" = "darkred", "MsDial_RT" = "darkgreen", "Unifi_RT" = "darkgrey")) + #colours of points
  labs( y = "Retention time [min]", x=expression(paste("Theoretical ",italic("m/z"), " values"))) +
  scale_y_continuous(limit=c(0,4),expand = c(0,0))+
  
  #geom_text(aes(x=mz, y=RT_softwares, label=compound), size=2, colour="red4",
  #             nudge_x = 0.25, nudge_y = 0.25, 
  #             check_overlap = FALSE)+
  
  theme_minimal()+
  theme(
    panel.background = element_rect(fill = "white"),  # Set white background
    panel.grid.major = element_blank(),  # Remove grid lines
    panel.grid.minor = element_blank(),  # Remove grid lines
    axis.text = element_text(size = 9),  # Increase font size of axis text
    axis.title.y = element_text(size = 9,face = "bold"),  # Make y-axis label bold and italic
    axis.text.y = element_text(color = "black", size = 9),  # Make x-axis text bold
    axis.title.x = element_text(size = 10,face = "bold"),
    axis.text.x = element_text(color = "black", size = 9),  # Make x-axis text bold
    axis.ticks.x = element_line(color = "black"),  # Add ticks to x-axis in black color
    axis.ticks.y = element_line(color = "black"),  # Add ticks to y-axis in black color
    #aspect.ratio = 1,  # Set aspect ratio
    plot.margin = margin(0.5, 0.5, 0.4, 0.5, "cm"),  # Set plot margins
    legend.text=element_text(size=9),
    #legend.position = c(0.85, 0.85),
    legend.background = element_rect(fill="white",
                                   size=0.5, linetype="solid", 
                                   colour ="black"),
    legend.title = element_blank(),
    #legend.margin = margin(0.001, 1, 0.5, 0.5)
)

b + geom_label(data=rt_difference, mapping=aes(x=mz, y=MsDial_RT, label=compound),
              size=2, colour="black",
              nudge_x = 0.25, nudge_y = 0.15) 
```

```{r}
d <- ggplot(data=dt_difference_long, mapping=aes(x=mz, y=DT_softwares))+
  geom_bar(stat = "identity",position=position_dodge(), aes(fill=software_name))+
  
  scale_fill_manual(values = c("MzMine_DT" = "darkred", "MsDial_DT" = "darkgreen", "Unifi_DT" = "darkgrey")) +
  labs( y = "Drift Time [ms]", x=expression(paste("Theoretical ",italic("m/z"), " values"))) +
  scale_y_continuous(limit=c(0,10),expand = c(0,0))+ #removes the gap between the bars and the x-axis
  

  geom_line(data=dt_difference, color="black", aes(x=mz, y=Unifi_DT),size = 0.5, linetype = "dashed")+ #plots black line for Unifi_DT
  
  theme_minimal()+
  theme(
    panel.background = element_rect(fill = "white"),  # Set white background
    panel.grid.major = element_blank(),  # Remove grid lines
    panel.grid.minor = element_blank(),  # Remove grid lines
    axis.text = element_text(size = 9),  # Increase font size of axis text
    axis.title.y = element_text(size = 9,face = "bold"),  # Make y-axis label bold and italic
    axis.text.y = element_text(color = "black", size = 9),  # Make x-axis text bold
    axis.title.x = element_text(size = 10,face = "bold"),
    axis.text.x = element_text(color = "black", size = 9),  # Make x-axis text bold
    axis.ticks.x = element_line(color = "black"),  # Add ticks to x-axis in black color
    axis.ticks.y = element_line(color = "black"),  # Add ticks to y-axis in black color
    plot.margin = margin(0.5, 0.5, 0.4, 0.5, "cm"),  # Set plot margins
    legend.text=element_text(size=9),
    legend.background = element_rect(fill="white",
                                   size=0.5, linetype="solid", 
                                   colour ="black"),
    legend.title = element_blank(),
)

d + geom_label(data=dt_difference, mapping=aes(x=mz-10, y=MzMine_DT, label=compound),
              size=2, colour="black", nudge_y = 0.7, 
              ) #hjust="inward"
```

------------------------------------------------------------------------

------------------------------------------------------------------------

## Drug mixture

To compare the drug mixture (200 ppb) measured in ESI(+)-LC-IMS-HRMS (MSe mode, HDMSe). Data is from old settings and new setting that is supposed to be more suitable for labile compounds.

```{r}
#library(tidyverse), library(readxl), library(ggrepel), library(ggpubr)
data_drugmix <- read_csv("~/Project/hrms_converter-2024/new_old_settings_drugmix_featurelist_MzMine.csv", show_col_types = FALSE) |> 
  select(-`charge`,-`fragment_scans`,-`alignment_scores:rate`, -`alignment_scores:aligned_features_n`,-`alignment_scores:align_extra_features`,-`alignment_scores:weighted_distance_score`,-`alignment_scores:mz_diff_ppm`,-`alignment_scores:mz_diff`,-`alignment_scores:rt_absolute_error`,-`alignment_scores:ion_mobility_absolute_error`,-`intensity_range:min`,-`intensity_range:max`)

target_drugs <- read_excel("~/Project/hrms_converter-2024/illicit drugs CS-IS_data.xlsx", na = "NA") |> 
  filter(Class=="Analyte") |> 
  mutate(rt_target_min = Vion_RT - 0.05) |> 
  mutate(rt_target_max = Vion_RT + 0.05) |> 
  select(-`Monoisomass`, -`Adduct_ion`,  -`Vion_observed_mz`, -`Agilent_observed_mz`, -`Agilent_RT`)


found_drugs <- target_drugs |> inner_join(data_drugmix, join_by(overlaps("Theor_adduct_mz","Theor_adduct_mz","mz_range:min", "mz_range:max"))) |> 
  select(1:11, mz, height, everything()) #reorder columns

#found_drugs |> filter(
#  !(is.na(Vion_RT) & `height` < 500), #removes those without RT that has height less than 500
#  !(!is.na(Vion_RT) & ("rt" < "rt_target_min" & "rt" > "rt_target_max")) #for those with RT, filter according to rt similarities
#)

filtered_found_drugs <-found_drugs |> filter(
  !(`height` < 500), #removes rows with height less than 500
  !(!is.na(Vion_RT) & ("rt" < "rt_target_min" & "rt" > "rt_target_max")) #for those with prev. measured RT, compares them with currect RT
) |> 
  slice_max(by=Compound, height) #to remove multiple features assigned the same compound by only keeping the ones with largest height. Due to not having any DT values to compare to filter the data more


filtered_found_drugs <- filtered_found_drugs |> 
  mutate(Mass_error_ppm = mass_error(Theor_adduct_mz, mz), .after = "mz")|>  #adds the mass error (calculated with the function) to a new column after m/z values
  mutate(height_ratio = `datafile:Drugdtd-200ppb-newsetting_1_A,2_1.mzML:height`/`datafile:Drugstd-200ppb_1_A,3_1.mzML:height`, .after="height") |> #adds the ratio between the height of the old and new settings 
  mutate(area_ratio = `datafile:Drugdtd-200ppb-newsetting_1_A,2_1.mzML:area`/`datafile:Drugstd-200ppb_1_A,3_1.mzML:area`, .after="area")


p1 <-ggplot(filtered_found_drugs, mapping = aes(x=mz, y=area_ratio, label=Compound))+ #plot area ratio
  geom_point()+
  geom_hline(yintercept = 1, linetype = "dashed", color = "red", linewidth = 0.1) + #adds horzontal line at y=0
  
  geom_label_repel(size = 2.5,
                   point.padding = NA, # additional padding around each point
                   min.segment.length = 0, # draw all line segments
                   force=2,
                   nudge_x=5, nudge_y=-0.03
                   )+
  
  theme_minimal()+
  theme(
    panel.background = element_rect(fill = "white"),  # Set white background
    panel.grid.major = element_blank(),  # Remove grid lines
    panel.grid.minor = element_blank(),  # Remove grid lines
    axis.text = element_text(size = 9),  # Increase font size of axis text
    axis.title.y = element_text(size = 9,face = "bold"),  # Make y-axis label bold and italic
    axis.text.y = element_text(color = "black", size = 9),  # Make x-axis text bold
    axis.title.x = element_text(size = 10,face = "bold"),
    axis.text.x = element_text(color = "black", size = 9),  # Make x-axis text bold
    axis.ticks.x = element_line(color = "black"),  # Add ticks to x-axis in black color
    axis.ticks.y = element_line(color = "black"),  # Add ticks to y-axis in black color
    plot.margin = margin(0.5, 0.5, 0.4, 0.5, "cm"),  # Set plot margins
    legend.text=element_text(size=9),
    legend.background = element_rect(fill="white",
                                   size=0.5, linetype="solid", 
                                   colour ="black"),
    legend.title = element_blank(),
)
p2 <- ggplot(filtered_found_drugs, mapping=aes(x=mz,y=height_ratio,label=Compound))+ #plot height ratio
  geom_point()+
  geom_hline(yintercept = 1, linetype = "dashed", color = "red", linewidth = 0.1) + #adds horzontal line at y=0
  
  geom_label_repel(size = 2.5,
                   point.padding = NA, # additional padding around each point
                   min.segment.length = 0, # draw all line segments
                   force=2,
                   nudge_x=5, nudge_y=-0.03
                   )+
  
  theme_minimal()+
  theme(
    panel.background = element_rect(fill = "white"),  # Set white background
    panel.grid.major = element_blank(),  # Remove grid lines
    panel.grid.minor = element_blank(),  # Remove grid lines
    axis.text = element_text(size = 9),  # Increase font size of axis text
    axis.title.y = element_text(size = 9,face = "bold"),  # Make y-axis label bold and italic
    axis.text.y = element_text(color = "black", size = 9),  # Make x-axis text bold
    axis.title.x = element_text(size = 10,face = "bold"),
    axis.text.x = element_text(color = "black", size = 9),  # Make x-axis text bold
    axis.ticks.x = element_line(color = "black"),  # Add ticks to x-axis in black color
    axis.ticks.y = element_line(color = "black"),  # Add ticks to y-axis in black color
    plot.margin = margin(0.5, 0.5, 0.4, 0.5, "cm"),  # Set plot margins
    legend.text=element_text(size=9),
    legend.background = element_rect(fill="white",
                                   size=0.5, linetype="solid", 
                                   colour ="black"),
    legend.title = element_blank(),
) 

ggarrange(p1, p2,
          labels = c("A", "B"),
          #ncol = 1, nrow = 2,
          widths = 2, heights = 10)

```

```{r}
target_IS <- read_excel("~/Project/hrms_converter-2024/illicit drugs CS-IS_data.xlsx", na = "NA") |> 
  filter(Class=="IS") |> 
  select(-`Monoisomass`, -`Adduct_ion`,  -`Vion_observed_mz`, -`Agilent_observed_mz`, -`Agilent_RT`)


found_IS <- target_IS |> inner_join(data_drugmix, join_by(overlaps("Theor_adduct_mz","Theor_adduct_mz","mz_range:min", "mz_range:max"))) |> 
  select(1:11, mz, height, everything()) |>  #reorder columns 
  mutate(Mass_error_ppm = mass_error(Theor_adduct_mz, mz), .after = "mz")
  
filtered_found_IS <- found_IS |>  slice_min(by=Compound, abs(Mass_error_ppm)) #only keeps the rows with the smallest absolut mass error for each compound


normalisation_IS <- inner_join(x=filtered_found_drugs, y=filtered_found_IS, join_by(x$Formula == y$Formula)) |> 
  mutate(normalised_height_NEW = `datafile:Drugdtd-200ppb-newsetting_1_A,2_1.mzML:height.x`/`datafile:Drugdtd-200ppb-newsetting_1_A,2_1.mzML:height.y`, .after="height.x") |> 
  mutate(normalised_height_OLD = `datafile:Drugstd-200ppb_1_A,3_1.mzML:height.x`/`datafile:Drugstd-200ppb_1_A,3_1.mzML:height.y`, .after="height.x") |> 
  mutate(RT_diff = rt.x-rt.y, .after="rt.x") |> 
  mutate(mz_error_diff = Mass_error_ppm.x-Mass_error_ppm.y, .after="mz.x") |> 
  mutate(DT_diff = ion_mobility.x-ion_mobility.y, .after="ion_mobility.x")

######################################################################
normalisation_IS$plot <- NA #empy column to put plot in
plot_object <- ggplot(data = normalisation_IS, aes(x=normalised_height_OLD, y=normalised_height_NEW))+geom_point(colour="darkgreen")+theme_minimal()+theme(legend.position="none")  #create plot object to put in empty colum in the table

#library(gt) #package for makeing tables + library(gtExtras) # plot in table

#creates a table of selected column from normalisation_IS data
 gt_tab <- normalisation_IS |> select(Compound.x, Formula, RT_diff, DT_diff, mz_error_diff, normalised_height_OLD, normalised_height_NEW,plot) |> 
    gt() |>
   tab_options(table.font.color="black")|> 
    tab_header(
      title=md("**Drug mixture - 200 ppb**"), #**to make bold
      subtitle =md("For **new** and **old** MS settings analytes with corresponding *Internal Standard*") #* to make italic
      ) |> 
    fmt_number(columns = c(RT_diff, DT_diff, mz_error_diff,normalised_height_OLD, normalised_height_NEW), decimals=3) |>  #to formate numbers, can select specific columns to display certain nr. of deicmals for example. 
    tab_footnote(
    footnote = "Isomeric compounds. They have been matched to the same feature, hence, the reason for the identical values.",
    locations = cells_body(columns = Compound.x, rows = 1:2)
  ) |> 
    tab_footnote(
    footnote = md("The large mass error difference between *analyte* and *IS* is due to a larger mass error for the corresponding IS (10.9 compared to analyte -0.101)"),
    locations = cells_body(
      columns = mz_error_diff,
      rows = mz_error_diff == min((mz_error_diff))
    )
  ) |> 
    tab_row_group(
    label = md("*Methamphetamine-d9*"), #or can use gt(groupname_col="Compound.y") to add groupnames for all analytes
    rows = 1:2
  ) |> 
    tab_spanner(
    label = "Analyte Information",
    columns = c(Compound.x, Formula)
  ) |> 
    tab_spanner(
    label = md("Normalisation as <br> *analyte_height/IS_height*"),
    columns = c(normalised_height_OLD, normalised_height_NEW)
  )|> 
    tab_spanner(
    label = md("Differences as <br> *Analyte* - *IS*"),
    columns = c(RT_diff, DT_diff, mz_error_diff)
  ) |> 
    cols_label(
    Compound.x = html("Analyte Name"),
    Formula = html("Molecular formula"),
    RT_diff = html("Retention Time ,<br>min"),
    DT_diff = html("Drift Time ,<br>ms"),
    mz_error_diff = html("Mass Error,<br>ppm"),
    normalised_height_OLD = html("OLD"),
    normalised_height_NEW = html("NEW"),
  ) |> 
   tab_style(
    style = list(
      cell_fill(color = "lightcyan"),
      cell_text(weight = "bold")
      ),
    locations = cells_body(
      columns = normalised_height_OLD
    ) 
  ) |> 
     tab_style(
    style = list(
      cell_fill(color = "#F9E3D6"),
      cell_text(weight = "bold")
      ),
    locations = cells_body(
      columns = normalised_height_NEW
    ) 
  ) |> 
    tab_style(
    style = list(
      cell_text(color="red")
      ),
    locations = cells_body(
      columns = mz_error_diff,
      rows = mz_error_diff ==min((mz_error_diff))
    ) 
  )|> 
   text_transform(
     locations = cells_body(columns = plot),
     fn = function(x) {
       plot_object |> 
         ggplot_image((height=px(200)))
     }
   )
gt_tab
gt_tab |> gtsave(filename = "tab_1.html") #saves the table in HTML format
gt_tab |> gtsave(filename = "tab_1.tex") #saves the table in LaTEX format
gt_tab |> gtsave(filename = "tab_1.docx") #saves the table in WORD format



agg_iris = normalisation_IS  |> 
    group_by(Compound.x)  |> 
    reframe(
        normalised_height= list(normalised_height_OLD, normalised_height_NEW),
    )

agg_iris |> gt() |> gt_plt_sparkline(column = normalised_height)
```

------------------------------------------------------------------------

TidyMass

```{r}
source("https://www.tidymass.org/tidymass-packages/install_tidymass.txt")
install_tidymass(from = "tidymass.org")
```
